Multi-modality Imagery Database for Plant Phenotyping

### 2015-05-01 datapaper_intro.tex
revision by Jeff and Jin

With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to control plant growth is a key enabler~\cite{doos2002population}.
%
For this purpose, plant scientists make various genetic mutant strains of plants, grow them either in  growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally discover plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
%
While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.

@@

The objective of {\it plant visual phenotyping} is to analyze and categorize the visual appearance of plants. %~\cite{}.
In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
Today, motivated by the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{cruz2015depi}.
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.

>>>>

With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to influence plant growth is a key enabler~\cite{doos2002population}.
%
A classic genetics approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
%
While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.

@@

The objective of {\it plant visual phenotyping} is to analyze and categorize the visual appearance of plants. %~\cite{}.
In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
Today, motivated by the increasing lower cost and increasing diversity of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.
